SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-05-04 Chapters/Chapter01.tex
Hathor typos and grammar fixes.

    This is military-grade cryptography and full-blown paranoia.\\
    Whoever did it hears voices whispering `they know everything.' \\
    \medskip

    Other than that, it's a get-rich-quick-scheme \\
    that looks exactly like a get-rich-quick-scheme.}
	\\ \medskip
    --- Alex Linhares, EBAPE/FGV

@@

The primary problem for creating digital money is how to prevent double spending. As the money is digital, and copies can be made \textit{ad nauseam}, what can prevent counterfeiting? That is, what would prevent users from sending copies of the same money to two (or more) people? That is precisely the problem solved by Bitcoin and its underlying Blockchain technology. The current solution behind fiat money is having a single issuer, a central bank --- then trusting the financial institutions and regulators.

@@

The scaling problem is not precisely an issue of Bitcoin, but an issue of the Blockchain technology. Hence, all other Blockchain-based cryptocurrencies have the same limitations, such as Litecoin, Bitcoin Cash, and Ethereum. One may arguee that increasing the maximum block size is a feasible solution to scaling, but I would say that it is just a temporary solution which buys some time until the next network saturation.

Bitcoin seems to have the most decentralized network among the cryptocurrencies, even so, there are few miners and mining pools which together control over 50\% of the network’s computing (hash)power (for details, see \citet{gencer2018decentralization}). Hence, they have an oversized influence when it comes to changes in the Bitcoin protocol's behavior. They may also cooperate in an attack, avoiding transactions which seemed confirmed. The more decentralized, the more trustworthy Bitcoin is. This centralization problem is seem as an important challenge.

@@

After the launch of Bitcoin, more than 1,000 other cryptocurrencies have been created \citep{coinmarketcap}. In general, they are Bitcoin-like, which means they use similar technologies, including the blockchain. Some cryptocurrencies differs a lot from Bitcoin, like the ones which use the DAG model \citep{dagdiscussion2014, tangle2016, dagcoin2015, sompolinsky2013, lewenberg2015, vorick2015}. We are especially interested in one of them: Iota.

@@

Every transaction confirmed by the central coordinator is assumed to be valid and cannot be reverted. The remaining of the network can verify a confirmation through the central coordinator's digital signature. The coordinator will not be necessary anymore when the number of transactions per second reaches a minimum value, but Iota's developers cannot say precisely what is this minimum value. This just elucidates that the tangle does not seem to work properly under a low volume of transactions (and fluctuations in the number of transactions per second may severily affect Iota's trustworthy).

>>>>

    This is military-grade cryptography and full-blown paranoia.\\
    %Whoever did it hears voices whispering `they know everything.' \\
    \medskip

    Other than that, it's a get-rich-quick-scheme \\
    that looks exactly like a get-rich-quick-scheme.}
	\\ \medskip
    --- Alexandre Linhares, EBAPE/FGV

@@

The primary problem for creating digital money is how to prevent double spending. As the money is digital, and copies can be made \textit{ad nauseam}, what can prevent counterfeiting? What would prevent users from sending copies of the same money to two (or more) people? That is precisely the problem solved by Bitcoin and its underlying Blockchain technology. The current solution behind fiat money is having a single issuer, a central bank --- then trusting the financial institutions and regulators.

@@

The scaling problem is not precisely an issue of Bitcoin, but an issue of the Blockchain technology. Hence, all other Blockchain-based cryptocurrencies have the same limitations, such as Litecoin, Bitcoin Cash, and Ethereum. One may argue that increasing the maximum block size is a feasible solution to scaling, but I would say that it is just a temporary solution which buys some time until the next network saturation.

Bitcoin seems to have the most decentralized network among the cryptocurrencies, even so, there are few miners and mining pools which together control over 50\% of the network’s computing (hash)power (for details, see \citet{gencer2018decentralization}). Hence, they have an oversized influence when it comes to changes in the Bitcoin protocol's behavior. They may also cooperate in an attack, voiding transactions which seemed confirmed. The more decentralized, the more trustworthy Bitcoin is. This centralization problem is seen as an important challenge.

@@

After the launch of Bitcoin, more than 1,000 other cryptocurrencies have been created \citep{coinmarketcap}. In general, they are Bitcoin-like, which means they use similar technologies, including the blockchain. Some cryptocurrencies differs a lot from Bitcoin, like the ones which use the Directed Acyclic Graph (DAG) model \citep{dagdiscussion2014, tangle2016, dagcoin2015, sompolinsky2013, lewenberg2015, vorick2015}. We are especially interested in one of them: Iota.

@@

Every transaction confirmed by the central coordinator is assumed to be valid and cannot be reverted. The remaining of the network can verify a confirmation through the central coordinator's digital signature. The coordinator will not be necessary anymore when the number of transactions per second reaches a minimum value, but Iota's developers cannot say precisely what is this minimum value. This just elucidates that the tangle does not seem to work properly under a low volume of transactions (and fluctuations in the number of transactions per second may severily affect Iota's trustworthiness).

### 2018-05-04 Chapters/hathor-architecture.tex
Hathor typos and grammar fixes.

Both miners and users will be working on proof-of-work, decentralizing even more the network's hash rate. Even though the users' difficulty is less than the miners', the hash rate will increase every new user. The more transactions arrive, the higher the total hash rate. It may have good consequences in governance, which we will further discuss.

There is a trade-off about the difficulty of new transactions. The higher it is, the harder it is to generate new transactions, preventing spammers but also making it harder for IoT devices generate new transactions. This difficulty may even be increased when a spam attack is in course and reduced when it is gone. If the difficulty is too high, IoT devices may sign their transactions and send them to another devices which have a greater hash rate and will solve their proof-of-work faster.

It also seems interesting to have this difficulty depending on new transaction's size (in bytes) and amount being moved. The idea here is to require more work when high amounts are at stake. It would not affect IoT devices, which are expected to usually move smaller amounts. Regarding the transaction's size, requiring more work for bigger transactions may make sense because they may prevent abuses, such as a denial-of-service attack using enormous transactions which would consume a lot of node's bandwidth and disk space.

@@

The incentive scheme which keeps the network running is the same as Bitcoin's. Miners go towards fees and newly generate coins, whereas users just want to exchange their tokens. When there is no new transcation to be confirmed, the miners keep the network up and running while they find new blocks.

@@

Explain transient and stationary state. The balance happens in the stationary state.

In order to estimate the balance in the number of tips, let's consider the system in which the rate of inward tips is $\lambda_\text{TX}$, while the rate of outward tips is $\rho$. Let $K$ be the number of tips in the system. Thus, after $\Delta t$ seconds, $\Delta \text{tips} = \lambda_\text{TX} \Delta t - \rho K \Delta t$. In the balance, $\Delta \text{tips} = 0$, hence $K = \frac{\lambda_\text{TX}}{\rho}$.

Finally, the rate of outward tips is twice the rate in which devices solve the proof-of-work of transactions. Let $H$ be the devices' hash rate, then, $\rho = 2 \cdot H \cdot 2^{-w_\text{TX}}$.

Twice?! It is a number between 1 and 2, but none of them.

Therefore, in the balance,

@@

$$\frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{2H} \le K \le \frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{H}$$

\section{Attacks \& Conflicting transactions}

\section{Scripts \& Contracts}

>>>>

Both miners and users will be working on proof-of-work, decentralizing even more the network's hash rate. Even though the users' difficulty is less than the miners', the hash rate will increase with every new user. The more transactions arrive, the higher the total hash rate. This may have good consequences in governance, which we will further discuss.

There is a trade-off about the \textit{difficulty} of new transactions. The higher it is, the harder it is to generate new transactions, preventing spammers but also making it harder for IoT devices generate new transactions. This difficulty may even be increased when a spam attack is in course and reduced when it is gone. If the difficulty is too high, IoT devices may sign their transactions and send them to another devices which have a greater hash rate and will solve their proof-of-work faster.

It also seems interesting to have this difficulty depending on new transaction's size (in bytes) and amount being moved. The idea here is to require more work when high amounts are at stake. It would not affect IoT devices, which are expected to usually move smaller amounts. Regarding the transaction's size, requiring more work for larger transactions may make sense because they may prevent abuses, such as a denial-of-service attack using enormous transactions which would consume a lot of node's bandwidth and disk space.

@@

The incentive scheme which keeps the network running is the same as Bitcoin's. Miners go towards fees and newly generate coins, whereas users just want to exchange their tokens. When there is no new transaction to be confirmed, the miners keep the network up and running while they find new blocks.

@@

It is intuitive that the number of tips depends on the number of transactions per second. The higher the number of transactions per second, the higher the number of tips. We can model the number of tips at time $t$ as a stochastic process, which means it changes over time following some probability distribution. Stochastic processes have two important states: transient and steady. A process is in transient state when its properties are changing over time, whereas it is in steady state when its properties has already converged.

Let's assume that the number of transactions per second is constant and does not change over time. Thus, at the beginning, there will be no tips, and the number will increase until it converges to its stable quantity. The process is in transient state until it reaches the stability. Then, it reaches the steady state. Notice that the number of tips also change in steady state, but its average does not change. It just floats around the average.

If the number of transactions per second increases, the process returns to the transient state and moves towards the new steady state. In practice, the number of transactions per second is always changing, so is the steady state.

In order to estimate the number of tips in the steady state, let's consider the process in which the rate of inward tips is $\lambda_\text{TX}$, while the rate of outward tips is $\rho$. Let $K$ be the number of tips at a given time. Thus, after $\Delta t$ seconds, $\Delta \text{tips} = \lambda_\text{TX} \Delta t - \rho K \Delta t$. In the steady state, $\Delta \text{tips} = 0$, hence $K = \frac{\lambda_\text{TX}}{\rho}$.

Finally, the rate of outward tips is twice the rate in which devices solve the proof-of-work of transactions. Let $H$ be the devices' hash rate, then, $\rho = 2 \cdot H \cdot 2^{-w_\text{TX}}$.
%Twice?! It is a number between 1 and 2, but none of them.

Therefore, in the steady state,

@@

%$$\frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{2H} \le K \le \frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{H}$$
For further information about the stochastic process of the total number of tips, see \citet{tangle2016}.

%\section{Attacks \& Conflicting transactions}
%\section{Scripts \& Contracts}
